Quasicharacters and the function-sheaf dictionary

### 2014-09-10 crelle-dictionary.tex
Good progress on adapting bibliography to Crelle style
Finished updating bibliography to crelle style using amsrefs and Bibtex database

%%%%%%%%%%%%%%%%% PACKAGES %%%%%%%%%%%%%%%%%
% Encodings
%\usepackage[utf8]{inputenc}
%\usepackage[T1]{fontenc}
% AMS packages
%\usepackage{amsmath, amsthm, amssymb}
\usepackage{todonotes}%, showkeys}
\usepackage{amsrefs}
\BibSpec{lecture}{%
  +{}{\PrintAuthors} {author}
  +{,}{ \textit} {title}
  +{}{ \parenthesize} {date}
  +{,}{ } {note}
  +{,}{ } {location}
  +{.}{ } {transition}
}
\BibSpec{preprint}{%
  +{}{\PrintAuthors} {author}
  +{,}{ \textit} {title}
  +{,}{ preprint } {date}
  +{,}{ } {note}
  +{.}{ } {transition}
}
% Fonts
\usepackage{mathrsfs}
%\usepackage{yfonts}
%Geometry
%\usepackage{geometry}
% Enumitem
\usepackage{enumitem}
% TikZ
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,calc,matrix}
\usepackage{tikz-cd}
% Hyperrefs
\usepackage{hyperref}

@@

The zeroth page of the Hochschild-Serre spectral sequence
is a double complex $E^{\bullet, \bullet}$ defined by
\[
E^{i,j} = C^i(\Weil{}, C^j(G(\bFq), \EEx));
\]
see \cite{Vakil:spectral_sequences}, expanding on \cite{Weibel:Homological_Algebra}*{Ch 5 and \S 7.5}.
The standard derivative on cochains yields two derivatives,
\begin{align*}
d_G &: E^{i,j} \to E^{i,j+1} \quad \mbox{and} \\
d_{\Weil{}} &: E^{i,j} \to E^{i+1,j};
\end{align*}
we use the first as the derivative $d_0$ on the zeroth page, and the second to induce $d_1$.
Combining them also yields a derivative $d = d_G + (-1)^j d_{\Weil{}}$ on the total complex
\[
E^n_G = \bigoplus_{i+j=n} E^{i,j}.
\]
The machinery of spectral sequences gives us a sequence of pages $E_r^{i,j}$, converging to a page $E_{\infty}^{i,j}$. We summarize the key properties of this spectral sequence in the following proposition.

@@

Let $R$ be the ring of integers of $K$.
Write $\m$ for the maximal ideal of $R$ and set $R_n = R/\m^{n+1}$ for every non-negative integer $n$.
Suppose $X_K \in \mathcal{N}_K$ has N\'eron model $X$ over $R$.
Note that $X(K) = X(R)$.
A \emph{quasicharacter of $X(K)$} is a group homomorphism $X(K) \to \EEx$ that factors through $X(R) \to X(R_n)$ for some non-negative integer $n$.
We note that this use of the term is compatible with the use of the term {\it quasicharacter} in \cite{cassels-frohlich:AlgebraicNumberTheory}*{Ch XV, \S 2.3}.
The group of quasicharacters of $X(K)$ will be denoted by 
\[
\Hom_\text{qc}(X(K),\EEx)
\]
 and the subgroup of those that factor through $X(R_n)$ will be denoted by 
 \[
 \Hom_n(X(K),\EEx).
\]
In this section we will see how to geometrize and categorify quasicharacters of $X(K)$ using quasicharacter sheaves.

@@

%-------------------------------------------------------------------------%
% BIBLIOGRAPHY                                                            %
% References should be collected at the end of the paper and numbered in  %
% alphabetical order of the authors' names. Titles of journals should be  %
% abbreviated as in Mathematical Reviews. Please do not use small caps    %
% for the names of the authors. The preferred style is shown in the       %
% examples below.                                                         %
% Refer to the bibliography entries using \cite commands.                 %
% Using BibTeX, you simply have to add the names of your databases as     %
%   \bibliography{mydatabase}                                             %
% The file crelle.bst then ensures the correct style.                     %
%-------------------------------------------------------------------------%
%\bibliographystyle{amsalpha}
%\bibliography{../bibliography/Biblio}

\begin{bibdiv}
\begin{biblist}
%\bibselect{references}

\bib{beilinson-bernstein-deligne:81a}{article}{
   author={\it A. A. Be{\u\i}linson},
   author={\it J. Bernstein},
   author={\it P. Deligne},
   title={\rm Faisceaux pervers},
   journal ={Ast\'erisque},
   volume={100},
   publisher={Soc. Math. France},
   place={Paris},
   date={1982},
   pages={5--171},
%conference={
%      title={Analyse et topologie sur les espaces singuliers, I},
%      address={Luminy},
%      date={1981},
%   }
}

\bib{bernstein:vogan_conference}{lecture}{
	author = {\it J. Bernstein},
	title = {\rm Stacks in Representation Theory: What is a representation of an algebraic group?},
 note={Lecture delivered at {\it A conference dedicated to David Vogan on his 60th birthday: Representations of reductive groups}}, 
 %\url{http://math.mit.edu/conferences/Vogan/}},
 	date={May, 2014},
 	location={MIT, Boston},
 }

 \bib{bernstein-luntz:equivariant_sheaves}{book}{
      author={\it J. Bernstein},
      author={\it V. Luntz},
       title={\rm Equivariant sheaves and functors},
      series={Lecture Notes in Mathematics},
   publisher={Springer-Verlag},
     address={Berlin},
        date={1994},
      volume={1578},
}

\bib{bertrapelle-gonzales:Greenberg}{preprint}{
      author={\it A. Bertrapelle},
      author={\it C.-D. Gonz\'ales-Avil\'es},
       title={\rm The Greenberg functor revisited},
        note={\url{http://arxiv.org/abs/1311.0051}},
      date={2013},
}

\bib{bitan:discriminant}{article}{
      author={\it R. A. Bitan},
       title={\rm The discriminant of an algebraic torus},
        date={2011},
     journal={J. Number Theory},
      volume={131},
      number={9},
       pages={1657\ndash 1671},
}

\bib{bosch-lutkebohmert-reynaud:NeronModels}{book}{
      author={\it S. Bosch},
      author={\it W. L\"utkebohmert},
      author={\it M. Reynaud},
       title={\rm N\'eron models},
   publisher={Springer-Verlag},
     address={Berlin},
        date={1980},
}

\bib{brown:CohomologyGrps}{book}{
      author={\it K. S. Brown},
       title={\rm Cohomology of groups},
      series={Graduate Texts in Mathematics 87},
   publisher={{Springer-Verlag}},
     address={New York},
        date={1982},
}

\bib{cartan-eilenberg:HomologicalAlgebra}{book}{
      author={\it H. Cartan},
      author={\it S. Eilenberg},
       title={\rm Homological algebra},
   publisher={Princeton U.P.},
     address={Princeton},
        date={1956},
}

\bib{cassels-frohlich:AlgebraicNumberTheory}{book}{
      editor={\it J. W. S. Cassels},
      editor={\it A. Frohlich},
       title={\rm Algebraic number theory},
     edition={2nd ed.,},
   publisher={London Math Society},
     address={London},
        date={2010},
}

\bib{chai-yu:01a}{article}{
      author={\it C.-L. Chai},
      author={\it J.-K. Yu},
       title={\rm Congruences of N\'eron models for tori and the Artin
  conductor},
        date={2001},
     journal={Annals of Math},
      volume={154},
      number={2},
       pages={347\ndash 382},
}

\bib{deligne:SGA4.5}{book}{
      author={\it P. Deligne},
       title={\rm Cohomologie \'Etale},
      series={{Lecture Notes in Mathematics 569}},
   publisher={{Springer-Verlag}},
     address={Berlin},
        date={1977},
}

\bib{deligne:80a}{article}{
      author={\it P. Deligne},
       title={\rm La conjecture de Weil II},
        date={1980},
     journal={{Inst. Hautes \'Etudes Sci. Publ. Math.}},
      volume={52},
       pages={137\ndash 252},
}

\bib{deligne:02a}{article}{
      author={\it P. Deligne},
       title={\rm {Cat\'egories tensorielles}},
        date={2002},
     journal={{Mosc. Math. J.}},
      volume={2},
      number={2},
       pages={227\ndash 248},
}

\bib{deligne-katz:SGA7.2}{book}{
      author={\it P. Deligne},
      author={\it N. Katz},
       title={\rm {Groupes de monodromie en g\'eom\'etrie alg\'ebrique. II}},
      series={{Lecture Notes in Mathematics}},
   publisher={{Springer-Verlag}},
     address={Berlin},
        date={1973},
      volume={340},
}

\bib{demazure-gabriel:GroupesAlgebriques}{book}{
      author={\it M. Demazure},
      author={\it P. Gabriel},
       title={\rm {Groupes alg\'ebriques. Tome 1: G\'eom\'etrie alg\'ebrique,
  g\'en\'eralit\'es, groupes commutatifs}},
   publisher={{Masson \& Cie}},
     address={Paris},
        date={1970},
        note={(Appendix: {\it M. Hazewinkel}, Corps de classes local)},
}

\bib{etingof:09a}{unpublished}{
      author={\it P. Etingof},
      author={\it S. Gelaki},
      author={\it D. Nikshych},
      author={\it V. Ostrik},
       title={\rm Tensor categories},
        date={2009},
        note={{Lecture notes for MIT's 18.769}, available at \url{http://www-math.mit.edu/~etingof/tenscat.pdf}},
}

\bib{vdGeer-Moonen:AbelianVarieties}{preprint}{
      author={\it G. van der Geer},
      author={\it B. Moonen},
       title={\rm {Abelian varieties}},
        date={2013},
       note={available at \url{http://staff.science.uva.nl/~bmoonen/boek/BookAV.html}},
%        note={Writing in progress.},
}

\bib{greenberg:61}{article}{
      author={\it M. J. Greenberg},
       title={\rm {Schemata over local rings I}},
        date={1961},
     journal={Annals of Math},
      volume={73},
      number={2},
       pages={624\ndash 648},
}

\bib{greenberg:63a}{article}{
      author={\it M. J. Greenberg},
       title={\rm {Schemata over local rings II}},
        date={1963},
     journal={Annals of Math},
      volume={78},
      number={2},
       pages={256\ndash 266},
}

\bib{EGAIV2}{article}{
      author={\it A. Grothendieck},
       title={\rm {\'El\'ements de g\'eom\'etrie alg\'ebrique. IV. \'Etude locale
  des sch\'emas et des morphismes de sch\'emas. II}},
        date={1965},
     journal={Inst. Hautes \'Etudes Sci. Publ. Math.},
      number={24},
}

\bib{EGAIV3}{article}{
   author={\it A. Grothendieck},
   title={\rm{\'El\'ements de g\'eom\'etrie alg\'ebrique. IV. \'Etude locale des
   sch\'emas et des morphismes de sch\'emas. III}},
   journal={Inst. Hautes \'Etudes Sci. Publ. Math.},
   number={28},
   date={1966},
}

\bib{SGA5}{book}{
      author={\it A. Grothendieck},
       title={\rm {S\'eminaire de G\'eom\'etrie Alg\'ebrique du Bois Marie 1965--66
  SGA5: Cohomologie $\ell$-adique et Fonctions L}},
      series={{Lecture Notes in Mathematics}},
   publisher={{Springer-Verlag}},
        date={1977},
      volume={589},
}

\bib{kamgarpour:09a}{article}{
      author={\it M. Kamgarpour},
       title={\rm {Stacky abelianization of algebraic groups}},
        date={2009},
     journal={{Transform. Groups}},
      volume={14},
      number={4},
       pages={825\ndash 846},
}

\bib{lang:56a}{article}{
      author={\it S. Lang},
       title={\rm{Algebraic groups over finite fields}},
        date={1956},
     journal={Amer. J. Math.},
      volume={78},
       pages={555\ndash 563},
}

\bib{laumon:87a}{article}{
      author={\it G. Laumon},
       title={\rm{Transformation de Fourier, constantes d'\'equations
  fonctionnelles et conjecture de Weil}},
        date={1987},
     journal={{Inst. Hautes \'Etudes Sci. Publ. Math.}},
      volume={65},
       pages={131\ndash 210},
}

\bib{lusztig:85a}{article}{
      author={\it G. Lusztig},
       title={\rm {Character Sheaves, I}},
        date={1985},
     journal={Advances in Math.},
      volume={56},
       pages={193\ndash 237},
}

\bib{lusztig:disconnected1}{article}{
      author={\it G. Lusztig},
       title={\rm {Character sheaves on disconnected groups. I}},
        date={2003},
     journal={Representation Theory},
      volume={7},
       pages={374\ndash 403},
}

\bib{nicaise-sebag:motivicSerre}{article}{
      author={\it J. Sebag},
      author={\it N. Nicaise},
       title={\rm{Motivic Serre invariants and Weil restriction}},
        date={2008},
     journal={J. Algebra},
      volume={319},
      number={4},
       pages={1585\ndash 1610},
}

\bib{Vakil:spectral_sequences}{unpublished}{
      author={\it R. Vakil},
       title={\rm{Spectral sequences: friend or foe?}},
        date={2008},
        note={Notes for 216: Foundations of Algebraic Geometry, available at \url{http://math.stanford.edu/~vakil/0708-216/216ss.pdf}},
}

\bib{vogan:93a}{article}{
   author={\it D. A. Vogan},
   title={\rm{The local Langlands conjecture}},
 %  conference={
 %     title={Representation theory of groups and algebras},
  % },
   journal ={Contemp. Math.},
    volume={145},
   publisher={Amer. Math. Soc.},
   place={Providence, RI},
   date={1993},
   pages={305--379},
}

\bib{Weibel:Homological_Algebra}{book}{
      author={\it C. A. Weibel},
       title={\rm{An introduction to homological algebra}},
      series={Cambridge Studies in Advanced Mathematics},
   publisher={Cambridge Univ. Press},
     address={Cambridge},
        date={1994},
      volume={38},
}

\end{biblist}
\end{bibdiv}

>>>>

%%%%%%%%%%%%%%%%% PACKAGES %%%%%%%%%%%%%%%%%
% Encodings
%\usepackage[utf8]{inputenc}
%\usepackage[T1]{fontenc}
% AMS packages
%\usepackage{amsmath, amsthm, amssymb}
\usepackage{todonotes}%, showkeys}
%\usepackage[numeric,initials]{amsrefs}
\usepackage{crellerefs}

% Fonts
\usepackage{mathrsfs}
%\usepackage{yfonts}
%Geometry
%\usepackage{geometry}
% Enumitem
\usepackage{enumitem}
% TikZ
\usepackage{tikz}
\usetikzlibrary{shapes,arrows,calc,matrix}
\usepackage{tikz-cd}
% Hyperrefs
\usepackage{hyperref}

@@

The zeroth page of the Hochschild-Serre spectral sequence
is a double complex $E^{\bullet, \bullet}$ defined by
\[
E^{i,j} = C^i(\Weil{}, C^j(G(\bFq), \EEx));
\]
see \cite{vakil:Algebraic_Geometry}*{\S 1.7}, expanding on \cite{weibel:Homological_Algebra}*{Ch 5 and \S 7.5}.
The standard derivative on cochains yields two derivatives,
\begin{align*}
d_G &: E^{i,j} \to E^{i,j+1} \quad \mbox{and} \\
d_{\Weil{}} &: E^{i,j} \to E^{i+1,j};
\end{align*}
we use the first as the derivative $d_0$ on the zeroth page, and the second to induce $d_1$.
Combining them also yields a derivative $d = d_G + (-1)^j d_{\Weil{}}$ on the total complex
\[
E^n_G = \bigoplus_{i+j=n} E^{i,j}.
\]
The machinery of spectral sequences gives us a sequence of pages $E_r^{i,j}$, converging to a page $E_{\infty}^{i,j}$. We summarize the key properties of this spectral sequence in the following proposition.

@@

Let $R$ be the ring of integers of $K$.
Write $\m$ for the maximal ideal of $R$ and set $R_n = R/\m^{n+1}$ for every non-negative integer $n$.
Suppose $X_K \in \mathcal{N}_K$ has N\'eron model $X$ over $R$.
Note that $X(K) = X(R)$.
A \emph{quasicharacter of $X(K)$} is a group homomorphism $X(K) \to \EEx$ that factors through $X(R) \to X(R_n)$ for some non-negative integer $n$.
We note that this definition is compatible with \cite{cassels-frohlich:AlgebraicNumberTheory}*{Ch XV, \S 2.3}.
The group of quasicharacters of $X(K)$ will be denoted by 
\[
\Hom_\text{qc}(X(K),\EEx)
\]
 and the subgroup of those that factor through $X(R_n)$ will be denoted by 
 \[
 \Hom_n(X(K),\EEx).
\]
In this section we will see how to geometrize and categorify quasicharacters of $X(K)$ using quasicharacter sheaves.

@@

%-------------------------------------------------------------------------%
% BIBLIOGRAPHY                                                            %
% References should be collected at the end of the paper and numbered in  %
% alphabetical order of the authors' names. Titles of journals should be  %
% abbreviated as in Mathematical Reviews. Please do not use small caps    %
% for the names of the authors. The preferred style is shown in the       %
% examples below.                                                         %
% Refer to the bibliography entries using \cite commands.                 %
% Using BibTeX, you simply have to add the names of your databases as     %
%   \bibliography{mydatabase}                                             %
% The file crelle.bst then ensures the correct style.                     %
%-------------------------------------------------------------------------%
\bibliography{bibliography/Biblio}
